Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-07 WSSSPE2_report/WSSSPE2_review.tex
small work in 7.1.3
very small work in 7.1.2

\subsubsection{First breakout discussion: Group B}
\note{writing in progress}
Discussion Extracts

Who to incentivize: 
Those in science (to do better, more shareable, more sustainable work).
Those in industry (but are interested in science).

@@

In the remaining discussion sessions, the group chose to split into three subgroups to discuss
a version of these topics: citation ecosystems,
taxonomy of contributorship/guidelines for software for tenure review, and prizes.

>>>>

\subsubsection{First breakout discussion: Group B}
\note{writing in progress}

This group started by discussing who should be incentivized, thinking of two categories of people:  
those in science (who could be incentivized to do better, more shareable, more sustainable work), and
those in industry but interested in science (who could be incentivized to contribute to science.)

@@

In the remaining discussion sessions, the group chose to split into three subgroups to discuss
a version of these topics: citation ecosystems,
taxonomy of contributorship/guidelines for software for tenure review, and prizes.  The subgroups were asked to clearly identify
\begin{itemize}
\item the problem to be solved
\item steps towards a solution
\end{itemize}
